Supplementary Material for Asymmetry paper

### 2020-02-26 Supplementary/Sup_mat.Rmd
New models and sup mat additions

---
title: "Supplementary Material for Asymmetry paper"
author: "Warren James"
date: "18/12/2019"
output: html_document
---

@@

```{r setup, include=T, message=F, warning=F}
# library 
library(tidybayes)
library(tidyverse)
```

## Experiment 1: Probability 
```{r Probability, include = F, echo = F}
# Load in everything from the modelling
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_like_dt")
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_like_dt_draws")
draws <- fix_like_post$draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  select(-estimate)
```

```{r Probability show plots, include = T, echo = F}
# Proportion fixations to most likely side 
plt_me_Bias <- draws %>% 
  ggplot(aes(prop,
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  theme(axis.title.x = element_blank()) +
  labs(fill = "Bias Type",
       colour = "Bias Type") +
#       "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

@@

```{r plots side fixations, echo = F, include = T}
# something like the first set of plots above 
plt_S_Dist <- df_prop_S %>% 
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank())

plt_S_Bias <- df_prop_S %>% 
  ggplot(aes(prop, 
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank())

plt_S_overall <- df_prop_S %>% 
  ggplot(aes(prop,
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  facet_wrap(~Dist_type) + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous("Proportion of Fixations to Most Likely Side",
                     labels = scales::percent_format(accuracy = 1)) +
  theme(axis.title.y = element_blank())

@@

# plt_difference 
plt_difference <- draws$Plots[3][[1]] + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat()

@@

## Reward

>>>>

---
title: "Supplementary Material for Asymmetry paper"
author: "Warren James"
output: 
  bookdown::pdf_document2:
    fig_caption: false
---

@@

```{r setup, include=T, message=F, warning=F}
# library 
library(tidybayes)
library(tidyverse)
library(brms)
```

# Resampling
For experiments 1, 3, and 4 we made use of resampling existing data as we had run experiments in the past that were comparable. Experiment 2 was slightly different in that we did not have previous data to compare to, as such, we generated a series of distributions based on previous data and how reliably we could detect small differences. Resampling was carried out in order to establish if adding more pariticipants to our sample sizes would have lead to a reduction in uncertainty around our estimates.

## Probability 
For this experiment, data from ($N$ = 12) Clark and Hunt (2016), which acted as a substitute for the Symmetric condition, and an unpublished pilot study ($N$ = 11), which followed the same rules as the Bias condition in the main experiment, were resampled in order to invesigate how often participants would fixate one of the side boxes given it was more likely to contain the target for the Bias condition. For the Symmetric condition, we followed the same rule as the in the paper and classified the most likely box as the side box that participants fixated most often. These data are shown in the box plots of the figure below. The main interest for our purposes was the proportion of time participants fixated the most likely box.

The data were coded so that a fixation was classified as either being to the Most likely box or not. We then resampled (with replacement) these data by selecting a random $N$ participants from each condition (ranging from 2 to 20) then sampling 300 trials from these participants from the different datasets. This was done 5000 times to estimate the expected difference between the Symmetric and Bias conditions in terms of proportion of fixations to the Most likely side and the associated certainty around these values.

As can be seen in the figure below, the uncertainty surrounding the estimate for the difference between the groups appears to plateau somewhere around 15 participants. The shaded region represents a 95% Highest Density Interval (HDI) for the disribution of differences simulated through resampling. As such, the sample size of 18 in the main experiment appears to be ample in order to detect this difference and increasing the sample size above this value does not add more to the certainty.

```{r load data, include = F, echo = F, message = F, warning = F}
load("../power/Prob_match/scratch/df_resample")
load("../power/Prob_match/scratch/df_sample")
```

```{r make plots, include = T, echo = F}
plt_data <- df_resample %>%  
  ungroup() %>% 
  group_by(Participant, Condition, Dist_type) %>% 
  mutate(centre = ifelse(box_type == "Centre", 1, 0),
         ML = ifelse(box_type == "Most", 1, 0),
         LL = ifelse(box_type == "Least", 1, 0),
         n = n()) %>%
  summarise(centre = mean(centre),
            ML = mean(ML),
            LL = mean(LL)) %>% 
  gather(centre:LL,
         key = "prop_type",
         value = "proportion") %>%
  mutate(prop_type = factor(prop_type, c("centre", "ML", "LL"),
                            labels = c("Centre", "Most Likely", "Least Likely"))) %>% 
  ggplot(aes(Dist_type, proportion,
             fill = Condition,
             colour = Condition)) + 
  geom_boxplot(alpha = .3) + 
  facet_wrap(~prop_type) +
  see::scale_color_flat() +
  see::scale_fill_flat() +
  theme_bw() +
  scale_x_discrete("Distance Type") +
  theme(axis.title.y = element_blank())

# maybe just the hdi stuff?
# do I want to rerun the sim with dist type added in?
plt_resampling <- df_sample %>% 
  spread(Condition, 
         Most) %>% 
  mutate(diff = Bias - Symmetric) %>% 
  group_by(n_sub) %>% 
  summarise(mu = mean(diff),
            lower = hdi(diff)[1],
            upper = hdi(diff)[2]) %>% 
  ggplot(aes(n_sub, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              alpha = .3) +
  theme_bw() + 
  scale_x_continuous("Sample Size") + 
  scale_y_continuous("Differenc in fixations to more \n likely side (Bias - Symmetric)")

gridExtra::grid.arrange(plt_data, plt_resampling)
```

## Hoop Sizes

Resampling for this experiment took the form of fitting a beta distribution to the _Throwing Experiment_ data from Clarke and Hunt (2016) using the fitdistrplus package. The values estimated using this procedure could were then adjusted to look at how reliably different sizes of effects could be detected. We altered the mean value but kept the variance the same to simulate participants shifting in one direction or the other. As can be seen in the figure below, we tested 4 different values (0.05, 0.1, 0.015, and 0.2) which were indicative of participants standing $X$\% closer to one side (in this case, in the direction of the smaller hoop). These ditributions were sampled from 5000 times by simulating $N$ participants (from 3 to 24) and simulating 72 trials. The plot below the distributions shows the uncertainty surrounding the mean estimate for the smallest difference tested (5\%). After 15 participants, the uncertainty surrounding the estimate appears to plateau which demonstrates that the sample size of 21 was sufficient to detect the effect. 
```{r load data and draw distributions, include = T, echo = F}
load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

# functions for getting parameters from a beta dist
mu_beta <- function(a, b){
  a/(a + b)
}
phi_beta <- function(a, b){
  1/((a*b)/(((a+b)^2)*(a+b+1)))
}
var_beta <- function(a, b){
  (a*b)/(((a+b)^2)*(a+b+1))
}

# get shape parameters 
get_shape_beta <- function(mu, var) {
  alpha <- ((1 - mu) / var - 1 / mu) * mu ^ 2
  beta <- alpha * (1 / mu - 1)
  return(params = list(alpha = alpha, beta = beta))
}

# sort out beta shape
shape_1 <- fitdistrplus::fitdist(df_part2$beta_pos, "beta")
mu1 <- mu_beta(shape_1$estimate[1], shape_1$estimate[2])
var1 <- var_beta(shape_1$estimate[1], shape_1$estimate[2])
shape_1 <- get_shape_beta(mu1, var1)
mu2 <- seq(0.05, .2, 0.05)
x <- seq(0,1,0.0005)

# draw these 
df_distributions <- tibble(x_vals = rep(x, length(c(0,mu2))),
                           base = mu1,
                           diff = rep(c(0,mu2), each = length(x)),
                           var = var1,
                           alpha = get_shape_beta(base + diff, var)$alpha,
                           beta = get_shape_beta(base + diff, var)$beta,
                           est_mu = mu_beta(alpha, beta),
                           est_var = var_beta(alpha, beta),
                           p = dbeta(x_vals, alpha, beta))
plt_distributions <- df_distributions %>% 
  mutate(diff = as.factor(diff)) %>%
  ggplot(aes(x_vals, p,
             colour = diff)) + 
  geom_line() + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "bottom")

plt_hdi <- df_sample %>% 
  filter(difference == 0.05) %>% 
  group_by(n_subs) %>% 
  mutate(diff = comparison - baseline) %>% 
  summarise(mu = mean(diff), 
            lower = hdi(diff)[1],
            upper = hdi(diff)[2]) %>% 
  ggplot(aes(n_subs, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              alpha = .3) + 
  scale_x_continuous("Sample Size") + 
  theme_bw() + 
  theme(axis.title.y = element_blank())

gridExtra::grid.arrange(plt_distributions, plt_hdi)
```

# Two Throws and Reward
As the hypothesis for both of these experiments was that out intervention would push participants towards being more optimal, we can use the same datasets to look at how uncertainty around the difference would change with varying sample sizes. For these experiments, comparison data was drawn from two unpublished studies; one in which the standard behaviour was observed, and one in which participants were closer to optimal in their performance.

The first dataset is comprised of 40 participants who took part in a version of the Clarke and Hunt (2016) _Throwing Task_. The second dataset is comprised of 60 participants who took part in a computerised version of this task. To compare these datasets, placement positions and standing positions were put on the same scale (0 being the centre and 1 being stood/placed next to the target). Only data for the easiest (smallest separataion of targets) and hard (furthest separation of targets) conditions were considered as these points offered more comparable base performance levels.

# Analysis

## Probability

```{r Probability, include = F, echo = F}
# Load in everything from the modelling
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_like_dt")
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_like_dt_draws")
draws <- fix_like_post$draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  select(-estimate)
```

```{r Probability show plots, include = T, echo = F, fig.cap = "posterior predictions for the probability matching experiment"}
# this is meant to add a figure caption but it looks terrible
# fig.cap="\\label{fig:fig1}Posterior predictions for the probability matching experiment"}
# Proportion fixations to most likely side 
plt_me_Bias <- draws %>% 
  ggplot(aes(prop,
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  theme(axis.title.x = element_blank()) +
  labs(fill = "Bias Type",
       colour = "Bias Type") +
  #       "Proportion of Fixations to Most Likely Side") +
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  scale_x_continuous(labels = scales::percent_format(accuracy = 1))

@@

```{r plots side fixations, echo = F, include = T}
# something like the first set of plots above 
plt_S_Dist <- df_prop_S %>% 
  ggplot(aes(prop,
             colour = Dist_type,
             fill = Dist_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) + 
  guides(fill = guide_legend(title = "Distance Type"),
         colour = guide_legend(title = "Distance Type"))

plt_S_Bias <- df_prop_S %>% 
  ggplot(aes(prop, 
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank()) + 
  guides(fill = guide_legend(title = "Bias Type"),
         colour = guide_legend(title = "Bias Type"))

plt_S_overall <- df_prop_S %>% 
  ggplot(aes(prop,
             colour = Bias_type,
             fill = Bias_type)) + 
  geom_density(alpha = .3) + 
  facet_wrap(~Dist_type) + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() +
  scale_x_continuous("Proportion of Fixations to Most Likely Side",
                     labels = scales::percent_format(accuracy = 1)) +
  theme(axis.title.y = element_blank()) + 
  guides(fill = guide_legend(title = "Bias Type"),
         colour = guide_legend(title = "Bias Type"))

@@

# plt_difference 
plt_difference <- draws$Plots[3][[1]] + 
  theme_bw() + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  guides(fill = guide_legend(title = "Distance"),
         colour = guide_legend(title = "Distance"))

@@

## Reward
```{r load in gambling data, include = F, echo = F, warning = F}
load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri")
load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri_draws")
draws_df <- draws_df %>% 
  mutate(prop = boot::inv.logit(estimate))

```

```{r make some plots, echo = F, inlude = T, warning = F}
# make separate plots for main effects and interactions 
plt_dist <- draws_df %>% 
  ggplot(aes(prop, 
             colour = Dist_Type,
             fill = Dist_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Distance Type"),
         fill = guide_legend(title = "Distance Type")) +
  scale_x_continuous("Normalised Position")

plt_gamble <- draws_df %>% 
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous("Normalised Position")

plt_inter <- draws_df %>%
  ggplot(aes(prop, 
             colour = Gamble_Type,
             fill = Gamble_Type)) + 
  geom_density(alpha = .3) + 
  see::scale_color_flat() + 
  see::scale_fill_flat() + 
  theme_bw() +
  guides(colour = guide_legend(title = "Gamble Type"),
         fill = guide_legend(title = "Gamble Type")) +
  scale_x_continuous("Normalised Position") + 
  facet_wrap(~Dist_Type)

gridExtra::grid.arrange(plt_dist, plt_gamble, plt_inter)

```
